Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2020-09-16 write-up/covid-writeup.tex
Update covid-writeup.tex

\begin{table}[!th]
\begin{tabular}{c | c | l l | l | l l }
& & \multicolumn{2}{c}{Total Tests} &  & \multicolumn{2}{c}{Positive Tests} \\
\cline{3-4} \cline{6-7}
& & NonRandom & Random & Census & NonRandom & Random \\ \hline
\multirow{2}{*}{Sex$^\star$} & Female & 57\% & 55\% & 49\% & 53\% & - \\
& Male & 43 & 45 & 51 & 47 & -  \\ \hline
\multirow{3}{*}{Age$^\star$} & $<40$ & 47 & 28 & 53 & 47\\
& $40-59$ & 28 & 36 & 25 & 3 0\\
& $\geq 60$ & 25 & 36 & 22 & 13\\ \hline
\multirow{2}{*}{Race$^\star$} & White & 60 & 98 & 85 & 50\\
& Nonwhite & 21 & 8 & 15 & 50 \\ \hline
\multirow{2}{*}{Symptoms$^{\star \star}$} & Yes & 62 & 43 & - & 83 & 62 \\
& No & 38 & 57 & - & 17 & 38  \\ \hline
\multirow{2}{*}{Contact$^{\star \star}$} & Yes & 11 & 1 & - \\
& No & 89 & 99 & - \\ \hline
\end{tabular}
\caption{Temp \\
$\star$: ISDH case-count nonrandom sample \\
$\star\star$: May 2--3 nonrandom sample
}
\end{table}

>>>>

\begin{table}[!th]
\begin{tabular}{c | c | l l | l | l l }
& & \multicolumn{2}{c}{Total Tests} & US & \multicolumn{2}{c}{Positive Test Rate}\\
\cline{3-4} \cline{6-7}
& & NonRandom & Random & Census & NonRandom & Random \\ \hline
\multirow{2}{*}{Sex} & Female & 58\% & 55\% & 51\% & 21.7\% & 1.42\% \\
& Male & 42 & 45 & 49 & 24.2 & 2.13 \\ \hline
\multirow{3}{*}{Age} & $<40$ & 40 & 28 & 53 & 29.7 & 1.71 \\
& $40-59$ & 41 & 36 & 25 & 24.9 & 2.09 \\
& $\geq 60$ & 19 & 36 & 22 & 6.7 & 0.92 \\ \hline
\multirow{2}{*}{Race} & White & 23 & 92 & 87 \\
& Nonwhite & 77 & 8 & 13 \\ \hline
\multirow{2}{*}{Symptom} & Yes & 62 & 43 & - &  \\
& No & 38 & 57 & - & \\ \hline
\multirow{2}{*}{Contact} & Yes & 11 & 1 & - \\
& No & 89 & 99 & - \\ \hline
\multirow{2}{*}{Prior test} & Yes & 6 & 1 & - \\
& No & 94 & 99 & - \\ \hline
\end{tabular}
\caption{Temp}
\end{table}

Average between May 2nd and 3rd is 11.7\% statewide.  So we need to adjust all these estimates down and then re-weight.
